\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-03-30 to-do.tex
add major categories to to-do

December 30, 2015
\begin{itemize}
	\item From Chad: it's missing intersection with reality
		\begin{itemize}
			\item Well articulated question / paradox
		\end{itemize}
	\item From Ben
		\begin{itemize}
			\item It's particularly interesting that in the presence of a shock the governments will use the escape clause as intended but without a shock a lobby group would always `step into the breach' and cause it to be abused.  I would like to see the paper devote more attention to the conditions under which this problem arises and when it does not.
			\item `Withdrawal of equivalent concessions' (WEC).
				\begin{itemize}
					\item Zissimos (2007): a government `chooses the severity of its own punishment' by the extent of its initial deviation.  In that paper, I took WEC for granted and then played out trade liberalization according to its rules.  But this left open the question of why WEC made sense as an approach to punishment.  Now I'm wondering whether your framework offers an answer.
					\item Under WEC, it is worth deviating from the agreement in proportion to $s$ because your partner deviates to the same extent and that keeps the agreement on track; the point first made by Bagwell and Staiger (1990).
					\item But WEC might eliminate the incentive to respond to lobbying pressure $e$ because when your trade partner deviates by WEC this takes away from you exactly (in a symmetrical framework) what you gained from the lobby for implementing a deviation of that size.
					\item I would find an examination of WEC much more compelling that the approach to punishment that you currently discuss on page 20, whereby two bindings are negotiated: one that applies if the trade partner keeps to the agreement and one that applies if they deviate.  As far as I know this latter approach does not mirror at all the institutional features actually set out by the GATT/WTO.
				\end{itemize}
		\end{itemize}
\end{itemize}

\vskip.5in
Possible puzzle to explain: WEC has an effect here, and that effect is weakened by the change in EC rules during the Uruguay Round
\begin{itemize}
	\item Read Chad's ``Why Are Safeguards under the WTO So Unpopular?'' (World Trade Review 2002), at \url{C:\Users\Kristy\Dropbox\Research\PE_shocks\Literature\2016}
		\begin{itemize}
			\item Need to understand better what changed, both with safeguard and with other policy instruments
		\end{itemize}
	\item There is this drop off in usage of escape clause (EC) after Uruguay Round (UR) reforms, even though retaliation prohibited for first three years. Why, when retaliation goes \textit{away}?
	\item I'm not sure there's a way to make sense of Ben's point: in my set-up, government doesn't ``get'' something different from lobby than it does directly from the shock. Maybe it should.
		\begin{itemize}
			\item Government feels $\ga$ the same whether it's elevated because of $s$ or because of $e$
			\item What is the neutralizing that happens? Why would the government invoke EC when it knows that WEC is coming anyway? Because it's in another sector where it puts less weight right now?
		\end{itemize}
	\item Need to go to continuous value of EC tariff
		\begin{itemize}
			\item There will be optimal tariff for whatever value of $s$ is realized
				\begin{itemize}
					\item Not sure how fine I want to go with $s$
				\end{itemize}
			\item Lobby will choose its optimal level of $e$. Will this be constrained in any way? Probably not, if there isn't a fixed EC-binding.
		\end{itemize}
\end{itemize}

>>>>

March 30, 2016
\begin{enumerate}
	\item Motivation
		\begin{itemize}
			\item From Chad: it's missing intersection with reality
				\begin{itemize}
					\item Well articulated question / paradox
				\end{itemize}
		\end{itemize}
	\item More on escape clause / WEC
		\begin{itemize}
			\item It's particularly interesting that in the presence of a shock the governments will use the escape clause as intended but without a shock a lobby group would always `step into the breach' and cause it to be abused.  I would like to see the paper devote more attention to the conditions under which this problem arises and when it does not.
			\item `Withdrawal of equivalent concessions' (WEC).
				\begin{itemize}
					\item Zissimos (2007): a government `chooses the severity of its own punishment' by the extent of its initial deviation.  In that paper, I took WEC for granted and then played out trade liberalization according to its rules.  But this left open the question of why WEC made sense as an approach to punishment.  Now I'm wondering whether your framework offers an answer.
					\item Under WEC, it is worth deviating from the agreement in proportion to $s$ because your partner deviates to the same extent and that keeps the agreement on track; the point first made by Bagwell and Staiger (1990).
					\item But WEC might eliminate the incentive to respond to lobbying pressure $e$ because when your trade partner deviates by WEC this takes away from you exactly (in a symmetrical framework) what you gained from the lobby for implementing a deviation of that size.
					\item I would find an examination of WEC much more compelling that the approach to punishment that you currently discuss on page 20, whereby two bindings are negotiated: one that applies if the trade partner keeps to the agreement and one that applies if they deviate.  As far as I know this latter approach does not mirror at all the institutional features actually set out by the GATT/WTO.
				\end{itemize}
			\item Possible puzzle to explain: WEC has an effect here, and that effect is weakened by the change in EC rules during the Uruguay Round
			\item Read Chad's ``Why Are Safeguards under the WTO So Unpopular?'' (World Trade Review 2002), at \url{C:\Users\Kristy\Dropbox\Research\PE_shocks\Literature\2016}
				\begin{itemize}
					\item Need to understand better what changed, both with safeguard and with other policy instruments
				\end{itemize}
			\item There is this drop off in usage of escape clause (EC) after Uruguay Round (UR) reforms, even though retaliation prohibited for first three years. Why, when retaliation goes \textit{away}?
			\item I'm not sure there's a way to make sense of Ben's point: in my set-up, government doesn't ``get'' something different from lobby than it does directly from the shock. Maybe it should.
				\begin{itemize}
					\item Government feels $\ga$ the same whether it's elevated because of $s$ or because of $e$
					\item What is the neutralizing that happens? Why would the government invoke EC when it knows that WEC is coming anyway? Because it's in another sector where it puts less weight right now?
				\end{itemize}
			\item Need to go to continuous value of EC tariff
				\begin{itemize}
					\item There will be optimal tariff for whatever value of $s$ is realized
						\begin{itemize}
							\item Not sure how fine I want to go with $s$
						\end{itemize}
					\item Lobby will choose its optimal level of $e$. Will this be constrained in any way? Probably not, if there isn't a fixed EC-binding.
				\end{itemize}
			\end{itemize}
	\item One good idea / do too much
	\item BS2005 vs. MRC2007
	\item Structured differently from most papers
	\item Costly state verification
	\item Define $\ga$ before using it
	\item Take out repeats, especially of references to BS2005, rely to heavily on BS2005
	\item Scrub unnecessary references to weak bindings (since strong are now mostly gone)
\end{enumerate}
